---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# CatchmentTracker

<!-- badges: start -->
<!-- badges: end -->

The goal of CatchmentTracker is to track upstream catchments from a given point and classify the landuse of the resulting catchment and upstream catchments. This is done through generating several WFS queries to:  

+ Catchment Data: [Bureau of Meteorology (BOM) Geofabric Data](http://geofabric.bom.gov.au/documentation/)  
+ Landuse Data: [Terrestrial Ecosystem Research Network's Geoserver](https://geoserver.tern.org.au/geoserver/web/)

## Installation

Tthe development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("JustinCally/CatchmentTracker", ref = 'master')
```
## Example

This is a basic example which shows you how to solve a common problem:

```{r example, warning = FALSE}
library(CatchmentTracker)
## basic example code

latitude <- -37.8107306254817
longitude <- 144.943636530752

df <- data.frame(long = longitude, lat = latitude)

point <- sf::st_as_sf(df, coords = c("long", "lat"), crs = 4283)

catchments <- track_catchments(point = point)

landuse_df <- landuse_extract(catchments)

knitr::kable(landuse_df)
```

